\LARGE \bf Exploiting Non-Slip Wall Contacts \\ to Position Two Particles Using a Shared Input

### 2018-01-24 journalWallFriction/SwarmShapeControl.tex

\begin{abstract}
There are driving applications for large populations of tiny robots in robotics, biology, and chemistry.
These robots often lack onboard computation, actuation, and communication.
Instead, these ``robots''  are  particles carrying some payload and the particle swarm is controlled by a shared control input such as a uniform magnetic gradient or electric field.
%In previous works, we showed that the 2D position of each particle in such a swarm is controllable if the workspace contains a single obstacle the size of one particle.
In previous works, we showed that the individual 2D position of two particles in such a swarm is controllable in a rectangular workspace requiring non-slip wall contact. However, both in vivo and artificial environments are usually not rectangular. 
%This work extends that work to any polygonal workspace, and focus on extending the algorithm for circular workspaces. Then it extends the algorithm to 3D. Results are validated with simulations and with a magnetic setup using two steel half a millimeter balls.
This work extends the analysis to convex workspaces and 3D positioning. This paper also implements the algorithms using a hardware setup inspired by intestine anatomy.
%Requiring a small, rigid obstacle suspended in the middle of the workspace is a strong constraint, especially in 3D.
%Often particles are placed into an em
%This paper relaxes that constraint, and provides position control algorithms that only require non-slip wall contact in 2D.
%Both in vivo and artificial environments often have such boundaries.
%We assume that particles in contact with the boundaries have zero velocity if the shared control input pushes the particle into the wall.
%This paper provides a shortest-path algorithm for positioning a two-particle swarm, and a generalization to positioning an $n$-particle swarm.
%Results are validated with simulations and a hardware demonstration.

>>>>

\begin{abstract}

Steered particles offer a method for targeted therapy, interventions, and drug delivery in regions inaccessible by large robots.
Magnetic actuation has the benefits of requiring no tethers, being able to operate from a distance, and in some cases allows imaging for feedback (e.g. MRI).
Given three orthogonal magnetic fields, steering one particle in 3D is trivial. 
Adding additional particles to steer makes the system underactuated because there are more states than control inputs. 
The walls of in vivo and artificial environments often have surface roughness such that the particles do not move unless actuation pulls them away from the wall.
In previous works, we showed that the individual 2D position of two particles is controllable in a square workspace with non-slip wall contact. 
However, in vivo environments are usually not square. 
This work extends the previous work to convex workspaces and 3D positioning. 
This paper also implements the algorithms using a hardware setup inspired by intestine anatomy.

%There are driving applications for large populations of tiny robots in robotics, biology, and chemistry.
%These robots often lack onboard computation, actuation, and communication.
%Instead, these ``robots''  are  particles carrying some payload and the particle swarm is controlled by a shared control input such as a uniform magnetic gradient or electric field.
%In previous works, we showed that the 2D position of each particle in such a swarm is controllable if the workspace contains a single obstacle the size of one particle.
%In previous works, we showed that the individual 2D position of two particles in such a swarm is controllable in a rectangular workspace requiring non-slip wall contact. However, both in vivo and artificial environments are usually not rectangular. 
%This work extends that work to any polygonal workspace, and focus on extending the algorithm for circular workspaces. Then it extends the algorithm to 3D. Results are validated with simulations and with a magnetic setup using two steel half a millimeter balls.
%This work extends the analysis to convex workspaces and 3D positioning. This paper also implements the algorithms using a hardware setup inspired by intestine anatomy.
%Requiring a small, rigid obstacle suspended in the middle of the workspace is a strong constraint, especially in 3D.
%Often particles are placed into an em
%This paper relaxes that constraint, and provides position control algorithms that only require non-slip wall contact in 2D.
%Both in vivo and artificial environments often have such boundaries.
%We assume that particles in contact with the boundaries have zero velocity if the shared control input pushes the particle into the wall.
%This paper provides a shortest-path algorithm for positioning a two-particle swarm, and a generalization to positioning an $n$-particle swarm.
%Results are validated with simulations and a hardware demonstration.
